A Comparison of Graph Processing Systems

### 2020-09-15 documentation/paper/sections/overview/gemini.tex

Gemini is a framework for distributed graph processing \cite{Gemini}.
It was developed with the goal to deliver a generally better performance through efficient communication.
While most other distributed graph processing systems achieve very good results in the shared-memory area, they often deliver unsatisfactory results in distributed computing.
Furthermore, a well optimized single-threaded implementation often outperforms a distributed system.
Therefore it is necessary to not only focus on the performance of the computation but also of the performance of the communication.
Gemini tries to bridge the gap between efficient shared-memory and scalable distributed systems.
To achieve this goal, Gemini, in contrast to the other NUMA-aware frameworks discussed here, does not support shared-memory calculation, but chooses the distributed message-based approach from scratch.

>>>>

Gemini is a framework for distributed graph processing \cite{Gemini}.
It was developed with the goal to deliver a generally better performance through efficient communication.
While most other distributed graph processing systems achieve very good results in the shared-memory area, they often deliver unsatisfactory results in distributed computing.
Furthermore, a well optimized single-threaded implementation often outperforms a distributed system.
Therefore it is necessary to not only focus on the performance of the computation but also of the performance of the communication.
Gemini tries to bridge the gap between efficient shared-memory and scalable distributed systems.
To achieve this goal, Gemini, in contrast to the other frameworks discussed here, does not support shared-memory calculation, but chooses the distributed message-based approach from scratch.

### 2020-09-15 documentation/paper/sections/preliminiaries.tex

\subsection{Push and Pull Variants}
Many parallel graph algorithms, as well as the three we consider here, are implemented by iterating over vertices, or edges \cite{Galois}.
The respective vertex or edge, which is considered in an iteration, is also called \emph{active} vertex or edge.
Applying an operator to this \emph{active} vertex or edge is called an \emph{activity}.
This operator considers always only a local so called \emph{neighborhood} to the \emph{active} vertex or edge.
To this \emph{neighborhood} belong only vertices and edges, which are in the direct surrounding of the \emph{active} vertex or edge, which allows to parallelise the iteration relatively easy.

@@

\subsection{NUMA-awareness}
\todo{Section}

>>>>

\subsection{Push and Pull Variants}
Many parallel graph algorithms, as well as the three we consider here, are implemented by iterating over vertices, or edges \cite{tao}.
The respective vertex or edge, which is considered in an iteration, is also called \emph{active}.
Applying an operator to this \emph{active} vertex or edge is called an \emph{activity}.
This operator considers always only a local so called \emph{neighborhood} to the \emph{active} vertex or edge.
To this \emph{neighborhood} belong only vertices and edges, which are in the direct surrounding of the \emph{active} vertex or edge, which allows to parallelise the iteration relatively easy.

@@

\subsection{Hugepages}
\todo{Section schreiben}
\cite{hugepages}
